Statistical Inference Week 2
=============================

```{r echo=FALSE}
library(knitr)
opts_chunk$set(cache=T, echo=T, warning=F, message=F)
```

Suppose that diastolic blood pressures (DBPs) for men aged 35-44 are normally distributed with a mean of 80 (mm Hg) and a standard deviation of 10. 
About what is the probability that a random 35-44 year old has a DBP less than 70?

```{r}
pnorm(70, mean=80, sd=10)
```

Brain volume for adult women is normally distributed with a mean of about 1,100 cc for women with a standard deviation of 75 cc.
What brain volume represents the 95th percentile?

```{r}
qnorm(0.95, mean=1100, sd=75)
```

Refer to the previous question. Brain volume for adult women is about 1,100 cc for women with a standard deviation of 75 cc. 
Consider the sample mean of 100 random adult women from this population. What is the 95th percentile of the distribution of that sample mean?

```{r}
qnorm(0.95, mean=1100, sd=75/sqrt(100))
```

You flip a fair coin 5 times, about what's the probability of getting 4 or 5 heads?

```{r}
pbinom(3, size=5, prob=0.5, lower.tail=FALSE)
```

The respiratory disturbance index (RDI), a measure of sleep disturbance, for a specific population has a mean of 15 (sleep events per hour) and a standard deviation of 10. They are not normally distributed. Give your best estimate of the probability that a sample mean RDI of 100 people is between 14 and 16 events per hour?

```{r}
pnorm(16, mean=15, sd=10/sqrt(100))-pnorm(14, mean=15, sd=10/sqrt(100))
```

Consider a standard uniform density. The mean for this density is .5 and the variance is 1 / 12. You sample 1,000 observations from this distribution and take the sample mean, what value would you expect it to be near?

```{r}
mean(rnorm(1000, mean=0.5, sd=sqrt(1/12)))
```

The number of people showing up at a bus stop is assumed to be Poisson with a mean of 5 people per hour. You watch the bus stop for 3 hours. About what's the probability of viewing 10 or fewer people?

```{r}
ppois(10, lambda=5*3)
```
